The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-04-06 paper/sections/results.tex
add lamppost timing and reorder the timing tables
specify the type of examples for all animations
add nnz and sparsity plot; clean deprecated figures

\begin{table*}[h]
  \caption{Performance of, and parameters for the Shape Matching Element Method on all examples. All wall-clock timings are reported in seconds, physical  parameters are
  reported with appropriate units. $\rho$ is the applied density, \textbf{E} is the  Young's Modulus and $\mu$ is the Poisson's ratio.
  \textbf{Sample} is the time taken to sample and construct $\samp{\Jnurbs}$ and $\samp{\Pmatx}$, \textbf{Quad} is the time taken to generate quadrature points via raycasting,
  \textbf{Weights} is the time to compute blending weights, \textbf{Build $\Pi$} is the time to build the projection operator and  \textbf{Step} is the average time required to step the simulation (not including collision detection).
  }
  \label{tbl:perf}
  \begin{center}
  \begin{tabular}{l c c c c c c c c c c}
   \textbf{Example} & $|\vc{q}|$ & \textbf{Material}&  $\rho$(kg/m$^3$) & \textbf{E}(Pa) & $\mu$ &\textbf{Sample}(s) & \textbf{Quad}(s)& \textbf{Weights}(s) & \textbf{Build $\Pi$}(s)& \textbf{Step}(s)\\
   \hline 
   \rowcolor[HTML]{DAE8FC} 
   %\textbf{Cantilever (soft)}       & 564 & Jelly & $1 e^3$ & $1e^6$& 0.45 & $2.53 e^{-2}$ & $4.45 e^{-3}$ & $4.78 e^{-1}$ & $1.86 e^{-1}$ & $1.20 e^{0}$ \\
   %\textbf{Cantilever (stiff)}      & 564 & Rubber & $1 e^3$ & $5 e^6$ & 0.45 & $2.48 e^{-2}$ & $6.37 e^{-3}$ & $5.10 e^{-1}$ & $1.68 e^{-1}$ & $1.19 e^{0}$ \\
   \rowcolor[HTML]{DAE8FC} 
   \textbf{Rocket (soft)}           & 648 & Rubber & $1.27 e^3$ & $7 e^6$ & 0.4 & $2.83 e^{-2}$ & $5.62 e^{-3}$ & $5.58 e^{-1}$ & $6.83 e^{-2}$ & $1.26 e^{0}$ \\
   \textbf{Rocket (stiff)}          & 648 & Steel & $8 e^3$ & $2 e^{11}$ & 0.32 & $2.56 e^{-2}$ & $5.97 e^{-3}$ & $4.59 e^{-1}$ & $3.48 e^{-2}$ & $9.99 e^{-2}$ \\
   \rowcolor[HTML]{DAE8FC} 
   \textbf{Starship}                & 750 & Steel & $8 e^3$ & $2 e^{11}$ & 0.32 & $6.78 e^{-2}$ & $1.52 e^{-2}$ & $8.50 e^{-1}$ & $9.52 e^{-2}$ & $6.95 e^{-1}$ \\
   \textbf{Tire}                    & 1404 & Rubber/Steel & $2 e^3$/$3 e^3$ & $1 e^6$/$7 e^9$ & 0.47 / 0.35 & $1.74 e^{-1}$ & $1.32 e^{-2}$ & $1.82 e^{0}$ & $6.79 e^{-1}$ & $1.28 e^{1}$ \\
   \rowcolor[HTML]{DAE8FC} 
   \textbf{Chicken}                 & 1773 & Jelly & $1.27 e^3$ & $1 e^4$ & 0.47 & $9.19 e^{-1}$ & $2.31 e^{-2}$ & $3.38 e^{0}$ & $1.91 e^{0}$ & $1.08 e^{1}$ \\
   \textbf{Coffee mug}              & 1800 & Jelly & $1 e^3$ & $1 e^4$ & 0.47 & $4.18 e^{-1}$ & $2.87 e^{-2}$ & $3.77 e^{0}$ & $2.08 e^{0}$ & $1.19 e^{1}$  \\   
   \rowcolor[HTML]{DAE8FC} 
   \textbf{Castle}                  & 1872 & Jelly & $1.27 e^3$ & $2 e^3$ & 0.45 & $4.84 e^{-1}$ & $1.44 e^{-2}$ & $1.52 e^{0}$ & $5.78 e^{-1}$ & $8.02 e^{0}$ \\
   \textbf{Astronaut (soft)}       & 3609 & Rubber &  $1.27 e^3$  & $1 e^6$  & 0.47 & $2.47 e^{0}$ & $6.71 e^{-2}$ & $1.13 e^{1}$ & $1.09 e^{1}$ & $1.41 e^{1}$ \\
   \hline
  \end{tabular}
  \end{center}

@@

@@

\reftbl{perf} shows the size of all our examples along with performance statistics and relevant parameters.
Note that the individual parts of all models are \emph{not connected}, and no continuity constraints or constructive solid geometry operations have been applied. 
Rather, the SEM approach implicitly couples the boundary parts together to allow for seamless volumetric simulation. 
Models were created using Autodesk Fusion 360 \cite{AutodeskFusion360} and Rhinocerous 3D 7 \cite{mcneel-rhinoceros}. 
Please see the supplemental video for more animation results.

@@

>>>>

\begin{table*}[h]
  \setlength{\tabcolsep}{3pt}
  \caption{Performance of, and parameters for the Shape Matching Element Method on all examples. All wall-clock timings are reported in seconds, physical parameters are
  reported with appropriate units. $\rho$ is the applied density, \textbf{E} is the  Young's Modulus and $\mu$ is the Poisson's ratio.
  \textbf{Sample} is the time taken to sample and construct $\samp{\Jnurbs}$ and $\samp{\Pmatx}$, \textbf{Quad} is the time taken to generate quadrature points via raycasting,
  \textbf{Weights} is the time to compute blending weights, \textbf{Build $\Pi$} is the time to build the projection operator, \textbf{Step} is the average time required to step the simulation (not including collision detection)
  \revise{and \textbf{Nnz} is the ratio of nonzeros to the total number of elements in the stiffness matrix. }
  \revise{We use linearly implicit time integration on all examples and thus the number of step per frame is 1 in the simulation.}
  }
  \label{tbl:perf}
  \begin{center}
  \begin{tabular}{l c c c c c c c c c c c}
   \textbf{Example} & $|\vc{q}|$ & \textbf{Material}&  $\rho$(kg/m$^3$) & \textbf{E}(Pa) & $\mu$ &\textbf{Sample}(s) & \textbf{Quad}(s)& \textbf{Weights}(s) & \textbf{Build $\Pi$}(s) & \textbf{Step}(s) & \revise{\textbf{Nnz}(\%)} \\
   \hline 
   \rowcolor[HTML]{DAE8FC}
   %\textbf{Cantilever (soft)}       & 564 & Jelly & $1 e^3$ & $1e^6$& 0.45 & $2.53 e^{-2}$ & $4.45 e^{-3}$ & $4.78 e^{-1}$ & $1.86 e^{-1}$ & $1.20 e^{0}$ \\
   %\textbf{Cantilever (stiff)}      & 564 & Rubber & $1 e^3$ & $5 e^6$ & 0.45 & $2.48 e^{-2}$ & $6.37 e^{-3}$ & $5.10 e^{-1}$ & $1.68 e^{-1}$ & $1.19 e^{0}$ \\
   \rowcolor[HTML]{DAE8FC} 
   \textbf{Rocket (soft)}           & 648 & Rubber & $1.27 e^3$ & $7 e^6$ & 0.40 & $2.83 e^{-2}$ & $5.62 e^{-3}$ & $5.58 e^{-1}$ & $6.83 e^{-2}$ & $1.26 e^{0}$ & \revise{100} \\
   \textbf{Rocket (stiff)}          & 648 & Steel & $8 e^3$ & $2 e^{11}$ & 0.32 & $2.56 e^{-2}$ & $5.97 e^{-3}$ & $4.59 e^{-1}$ & $3.48 e^{-2}$ & $9.99 e^{-2}$ & \revise{100} \\
   \rowcolor[HTML]{DAE8FC} 
   \textbf{Starship}                & 750 & Steel & $8 e^3$ & $2 e^{11}$ & 0.32 & $6.78 e^{-2}$ & $1.52 e^{-2}$ & $8.50 e^{-1}$ & $9.52 e^{-2}$ & $6.95 e^{-1}$ & \revise{100} \\
   \textbf{Lamppost}                & 942 & Rubber & $3 e^3$ & $1 e^6$ & 0.40 & $1.28 e^{-1}$ & $1.27 e^{-2}$ & $1.89 e^{0}$ & $1.07 e^{0}$ & $2.22 e^{0}$ & \revise{56.38} \\
   \rowcolor[HTML]{DAE8FC} 
   \textbf{Tire}                    & 1404 & Rubber/Steel & $2 e^3$/$3 e^3$ & $1 e^6$/$7 e^9$ & 0.47/0.35 & $1.74 e^{-1}$ & $1.32 e^{-2}$ & $1.82 e^{0}$ & $6.79 e^{-1}$ & $1.28 e^{1}$ & \revise{92.5} \\
   \textbf{Chicken}                 & 1773 & Jelly & $1.27 e^3$ & $1 e^4$ & 0.47 & $9.19 e^{-1}$ & $2.31 e^{-2}$ & $3.38 e^{0}$ & $1.91 e^{0}$ & $1.08 e^{1}$ & \revise{100} \\
   \rowcolor[HTML]{DAE8FC} 
   \textbf{Coffee mug (soft)}       & 1800 & Jelly & $1 e^3$ & $1 e^4$ & 0.47 & $4.18 e^{-1}$ & $2.87 e^{-2}$ & $3.77 e^{0}$ & $2.08 e^{0}$ & $1.19 e^{1}$ & \revise{100} \\ 
   \textbf{Coffee mug (stiff)}      & 1800 & Rubber & $1 e^3$ & $4 e^7$ & 0.40 & $4.15 e^{-2}$ & $1.17 e^{-2}$ & $6.86 e^{-1}$ & $1.09 e^{-1}$ & $5.00 e^{-1}$  & \revise{81.42} \\ 
   \rowcolor[HTML]{DAE8FC} 
   \textbf{Castle}                  & 1872 & Jelly & $1.27 e^3$ & $2 e^3$ & 0.45 & $4.84 e^{-1}$ & $1.44 e^{-2}$ & $1.52 e^{0}$ & $5.78 e^{-1}$ & $8.02 e^{0}$ & \revise{100} \\
   \textbf{Grumpy}                  & 2010 & Jelly & $1 e^3$ & $1 e^4$ & 0.40 & $2.92 e^{-1}$ & $1.23 e^{-2}$ & $2.29 e^{0}$ & $2.89 e^{0}$ & $6.02 e^{0}$ & \revise{84.15} \\    
   \rowcolor[HTML]{DAE8FC} 
   \textbf{Astronaut (soft)}        & 3609 & Rubber &  $1.27 e^3$  & $1 e^6$  & 0.47 & $2.47 e^{0}$ & $6.71 e^{-2}$ & $1.13 e^{1}$ & $1.09 e^{1}$ & $1.41 e^{1}$ & \revise{49.04} \\
   \revise{\textbf{Squid}}          & \revise{4347} & \revise{Jelly} & \revise{ $1 e^3$ } & \revise{$2 e^4$ } & \revise{0.40} & \revise{$4.48 e^{-1}$} & \revise{$2.47 e^{-2}$} & \revise{$1.54 e^{1}$} & \revise{$4.48 e^{1}$} & \revise{$6.73 e^{0}$} & \revise{25.47} \\
   \rowcolor[HTML]{DAE8FC} 
   \hline
  \end{tabular}
  \end{center}

@@

% \begin{table*}[h]
%   \caption{Performance of, and parameters for the Shape Matching Element Method on all examples. All wall-clock timings are reported in seconds, physical parameters are
%   reported with appropriate units. $\rho$ is the applied density, \textbf{E} is the  Young's Modulus and $\mu$ is the Poisson's ratio.
%   \textbf{Sample} is the time taken to sample and construct $\samp{\Jnurbs}$ and $\samp{\Pmatx}$, \textbf{Quad} is the time taken to generate quadrature points via raycasting,
%   \textbf{Weights} is the time to compute blending weights, \textbf{Build $\Pi$} is the time to build the projection operator and  \textbf{Step} is the average time required to step the simulation (not including collision detection).
%   \revise{We use linearly implicit time integration on all examples and thus the number of step per frame is 1 in the simulation.}
%   }
%   \label{tbl:perf}
%   \begin{center}
%   \begin{tabular}{l c c c c c c c c c c}
%    \textbf{Example} & $|\vc{q}|$ & \textbf{Material}&  $\rho$(kg/m$^3$) & \textbf{E}(Pa) & $\mu$ &\textbf{Sample}(s) & \textbf{Quad}(s)& \textbf{Weights}(s) & \textbf{Build $\Pi$}(s)& \textbf{Step}(s) \\
%    \hline 
%    \rowcolor[HTML]{DAE8FC}
%    %\textbf{Cantilever (soft)}       & 564 & Jelly & $1 e^3$ & $1e^6$& 0.45 & $2.53 e^{-2}$ & $4.45 e^{-3}$ & $4.78 e^{-1}$ & $1.86 e^{-1}$ & $1.20 e^{0}$ \\
%    %\textbf{Cantilever (stiff)}      & 564 & Rubber & $1 e^3$ & $5 e^6$ & 0.45 & $2.48 e^{-2}$ & $6.37 e^{-3}$ & $5.10 e^{-1}$ & $1.68 e^{-1}$ & $1.19 e^{0}$ \\
%    \rowcolor[HTML]{DAE8FC} 
%    \textbf{Rocket (soft)}           & 648 & Rubber & $1.27 e^3$ & $7 e^6$ & 0.40 & $2.83 e^{-2}$ & $5.62 e^{-3}$ & $5.58 e^{-1}$ & $6.83 e^{-2}$ & $1.26 e^{0}$ \\
%    \textbf{Rocket (stiff)}          & 648 & Steel & $8 e^3$ & $2 e^{11}$ & 0.32 & $2.56 e^{-2}$ & $5.97 e^{-3}$ & $4.59 e^{-1}$ & $3.48 e^{-2}$ & $9.99 e^{-2}$ \\
%    \rowcolor[HTML]{DAE8FC} 
%    \textbf{Starship}                & 750 & Steel & $8 e^3$ & $2 e^{11}$ & 0.32 & $6.78 e^{-2}$ & $1.52 e^{-2}$ & $8.50 e^{-1}$ & $9.52 e^{-2}$ & $6.95 e^{-1}$ \\
%    \textbf{Lamppost}                & 942 & Rubber & $3 e^3$ & $1 e^6$ & 0.40 & $1.28 e^{-1}$ & $1.27 e^{-2}$ & $1.89 e^{0}$ & $1.07 e^{0}$ & $2.22 e^{0}$ \\
%    \rowcolor[HTML]{DAE8FC} 
%    \textbf{Tire}                    & 1404 & Rubber/Steel & $2 e^3$/$3 e^3$ & $1 e^6$/$7 e^9$ & 0.47/0.35 & $1.74 e^{-1}$ & $1.32 e^{-2}$ & $1.82 e^{0}$ & $6.79 e^{-1}$ & $1.28 e^{1}$ \\
%    \textbf{Chicken}                 & 1773 & Jelly & $1.27 e^3$ & $1 e^4$ & 0.47 & $9.19 e^{-1}$ & $2.31 e^{-2}$ & $3.38 e^{0}$ & $1.91 e^{0}$ & $1.08 e^{1}$ \\
%    \rowcolor[HTML]{DAE8FC} 
%    \textbf{Coffee mug (soft)}       & 1800 & Jelly & $1 e^3$ & $1 e^4$ & 0.47 & $4.18 e^{-1}$ & $2.87 e^{-2}$ & $3.77 e^{0}$ & $2.08 e^{0}$ & $1.19 e^{1}$  \\ 
%    \textbf{Coffee mug (stiff)}      & 1800 & Rubber & $1 e^3$ & $4 e^7$ & 0.40 & $4.15 e^{-2}$ & $1.17 e^{-2}$ & $6.86 e^{-1}$ & $1.09 e^{-1}$ & $5.00 e^{-1}$  \\ 
%    \rowcolor[HTML]{DAE8FC} 
%    \textbf{Castle}                  & 1872 & Jelly & $1.27 e^3$ & $2 e^3$ & 0.45 & $4.84 e^{-1}$ & $1.44 e^{-2}$ & $1.52 e^{0}$ & $5.78 e^{-1}$ & $8.02 e^{0}$ \\
%    \textbf{Grumpy}                  & 2010 & Jelly & $1 e^3$ & $1 e^4$ & 0.40 & $2.92 e^{-1}$ & $1.23 e^{-2}$ & $2.29 e^{0}$ & $2.89 e^{0}$ & $6.02 e^{0}$  \\    
%    \rowcolor[HTML]{DAE8FC} 
%    \textbf{Astronaut (soft)}        & 3609 & Rubber &  $1.27 e^3$  & $1 e^6$  & 0.47 & $2.47 e^{0}$ & $6.71 e^{-2}$ & $1.13 e^{1}$ & $1.09 e^{1}$ & $1.41 e^{1}$ \\
%    \textbf{Squid}                   & 4347 & Rubber &  $1 e^3$  & $2 e^4$  & 0.40 & $4.48 e^{-1}$ & $2.47 e^{-2}$ & $1.54 e^{1}$ & $4.48 e^{1}$ & $6.73 e^{0}$ \\
%    \rowcolor[HTML]{DAE8FC} 
%    \hline
%   \end{tabular}
%   \end{center}

%   \end{table*}

@@

\reftbl{perf} shows the size of all our examples along with performance statistics and relevant parameters. 
\revise{We also plot the sparsity patterns of several stiffness matrices in our examples in \reffig{stiffness_sparsity}. }
Note that the individual parts of all models are \emph{not connected}, and no continuity constraints or constructive solid geometry operations have been applied. 
Rather, the SEM approach implicitly couples the boundary parts together to allow for seamless volumetric simulation. 
We use quadratic deformation for all the animation results, except the rocket (stiff) and starship which use linear deformation.
Models were created using Autodesk Fusion 360 \cite{AutodeskFusion360} and Rhinocerous 3D 7 \cite{mcneel-rhinoceros}. 
Please see the supplemental video for more animation results.

@@

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/stiffness_sparsity.pdf}
  \caption{\revise{Our stiffness matrices can be sparse, while the corresponding matrix has to be dense in the traditional Boundary Element Method \cite{ArtDefo1999}. 
  Sparsity of our stiffness matrix is primarily determined by weight sparsity (number of non-zero weights at a given quadrature point) and polynomial order. }}
  \label{fig:stiffness_sparsity}
\end{figure}
